Quality Assesment of OpenStreetMap Footpath Data

### 2020-06-18 report/report.tex
Clarify that the analysis section deals with footpaths

Looking closer at the individual collision cases, the next conclusion is that most often it is actually a small part of a road that is responsible for the collision, and will need correction.
Now will follow an exemplifying calculation to support this claim.
Looking in tables \ref{table:road-collision} and \ref{table:road-collision-corrected}, note that before road extrusion, 3189 features and 7330 of their edges were intersecting some other feature.
This means that for each colliding road, on average 2.3 of its edges will be intersecting some other feature, thus bearing responsibility for the collision.
In total there are 26473 feautures and 6382579 edges, meaning that each road feature is on average contructed out of 241 edges.
Thus the percentage of edges colliding per road is on average roughly 0.95\%.
A similar calculation for the number of features that could not be corrected by translation yields that the number of colliding edges per feature is on average 1.2, and that the percentage of colliding edges per feature is 0.49\%.
Visual inspection of the cases where roads collide with other features has supported this.

After visual inspection, it was determined that all collision occurences can be almost exclusively classified into one of five categories.
These categories are explained in the list below, and each case is exemplified in figure \ref{fig:collision-cases}.
All these cases will create issues when generating the 3D mesh representation of the city.

@@

\subsection{Suggested algorithms for overlap correction}

All collision cases can be solved with relatively simply geometric algorithms. This section will present suggestions on algorithms that will resolve collisions by identifying individual colliding nodes and translating them, after which some degree of smoothing (such as linear interpolation) can be applied to preserve visual features. Cases 1 and 3-5 will be handled, while 2 will be left since case 2 collisions do not inherently cause feature overlap when extruding a 3D road mesh from the way edges. Thus it will be up to the individual developer to decide what to do with Case 2 collisions.

>>>>

Looking closer at the individual collision cases for footpaths, the next conclusion is that most often it is actually a small part of a path that is responsible for the collision, and will need correction.
Now will follow an exemplifying calculation to support this claim.
Looking in tables \ref{table:road-collision} and \ref{table:road-collision-corrected}, note that before road extrusion, 3189 features and 7330 of their edges were intersecting some other feature.
This means that for each colliding road, on average 2.3 of its edges will be intersecting some other feature, thus bearing responsibility for the collision.
In total there are 26473 feautures and 6382579 edges, meaning that each road feature is on average contructed out of 241 edges.
Thus the percentage of edges colliding per road is on average roughly 0.95\%.
A similar calculation for the number of features that could not be corrected by translation yields that the number of colliding edges per feature is on average 1.2, and that the percentage of colliding edges per feature is 0.49\%.
Visual inspection of the cases where roads collide with other features has supported this.

After visual inspection, it was determined that footpath all collision occurences can be almost exclusively classified into one of five categories.
These categories are explained in the list below, and each case is exemplified in figure \ref{fig:collision-cases}.
All these cases will create issues when generating the 3D mesh representation of the city.

@@

\subsection{Suggested algorithms for footpath overlap correction}

All footpath collision cases can be solved with relatively simply geometric algorithms. This section will present suggestions on algorithms that will resolve collisions by identifying individual colliding nodes and translating them, after which some degree of smoothing (such as linear interpolation) can be applied to preserve visual features. Cases 1 and 3-5 will be handled, while 2 will be left since case 2 collisions do not inherently cause feature overlap when extruding a 3D road mesh from the way edges. Thus it will be up to the individual developer to decide what to do with Case 2 collisions.
